IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/intro.tex
typo.

Information flow control (IFC) is a promising technique
that provides security
by tracking the flow of sensitive data through a system.
Untrusted code is confined so that it cannot exfiltrate data, except as
per an information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in dynamic information
flow control is implementation efficiency: when
information flow is tracked at a fine-grained level,
e.g., per value in the system, systems may incur
impractical runtime overhead~\cite{JSFlow}.
%
Moreover, the task of adding fine-grained IFC event to a simple language is
non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
such as JavaScript, this challenge becomes almost insurmountable.

>>>>

Information flow control (IFC) is a promising technique
that provides security
by tracking the flow of sensitive data through a system.
Untrusted code is confined so that it cannot exfiltrate data, except as
per an information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in dynamic information
flow control is implementation efficiency: when
information flow is tracked at a fine-grained level,
e.g., per value in the system, systems may incur
impractical runtime overhead~\cite{JSFlow}.
%
Moreover, the task of adding fine-grained IFC even to a simple language is
non-trivial~\cite{hritcu2013testing}; when considering a real-world language,
such as JavaScript, this challenge becomes almost insurmountable.
